Datasheet for the child care of working mothers dataset

### 2022-04-03 inputs/data/datasheet.Rmd
Update figure labels

---
title: "Datasheet for the child care of working mothers dataset"
subtitle: ""
author: 
  - Pascal Lee Slew
  - Yunkyung Park
thanks: "Code and data are available at: https://github.com/Pascal-304/dhs_analysis."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "The datasheet serves the purpose of documenting the creation of a dataset. It has two main objectives, one for data creators and the other for data consumers. For data creators, it allows the reflection on the data gathering and cleaning process. While for data consumers, it provides an understanding of how the dataset was created. The key idea behind it would be transparency and accountability."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references_datasheet.bib
---

@@

1. *Who will be supporting/hosting/maintaining the dataset?*
	- Yunkyung Park and Pascal Lee Slew
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- If anyone want to reach out to us about the dataset, you can contact us at clara.park@mail.utoronto.ca or pascal.leeslew@mail.utoronto.ca
3. *Is there an erratum? If so, please provide a link or other access point.*
	- No
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- If there is any error made in the creation of the dataset, the dataset will be updated by either Yunkyung Park or Pascal Lee Slew. Any updates will be communicated as a note in the Readme file at the link below: https://github.com/Pascal-304/dhs_analysis/blob/main/README.md
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- N/A
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- The dataset has just been created. If there are any updates, older versions will still be kept for consistency.
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- Others may do so and should contact the original authors about incorporating fixes/extensions.

>>>>

---
title: "Datasheet for the child care of working mothers dataset"
author: 
  - Pascal Lee Slew
  - Yunkyung Park
thanks: "Code and data are available at: https://github.com/Pascal-304/dhs_analysis."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "The datasheet serves the purpose of documenting the creation of a dataset. It has two main objectives, one for data creators and the other for data consumers. For data creators, it allows the reflection on the data gathering and cleaning process. While for data consumers, it provides an understanding of how the dataset was created. The key idea behind it would be transparency and accountability."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references_datasheet.bib
---

@@

1. *Who will be supporting/hosting/maintaining the dataset?*
	- Pascal Lee Slew and Yunkyung Park
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- If anyone want to reach out to us about the dataset, you can contact us at pascal.leeslew@mail.utoronto.ca or clara.park@mail.utoronto.ca
3. *Is there an erratum? If so, please provide a link or other access point.*
	- No
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- If there is any error made in the creation of the dataset, the dataset will be updated by either Yunkyung Park or Pascal Lee Slew. Any updates will be communicated as a note in the Readme file at the link below: https://github.com/Pascal-304/dhs_analysis/blob/main/README.md
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- N/A
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- The dataset has just been created. If there are any updates, older versions will still be kept for consistency.
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- Others may do so and should contact the original authors about incorporating fixes/extensions.
